---
title: "Activity: Popular Names"
author: "Eric weah"
date: "2/23/2020"
output: html_notebook
---



# Set Up

```{r}
# load necessary packages
library(tidyverse)
library(mosaic)
library(DataComputing)
```


```{r}
# Load the BabyNames data into RStudio environment (from DataComputing package)
data("BabyNames")

```

# Activity

**Goal**: By the end of the activity, each team will create a graph (like Figure A.1 on p 159) showing ups and downs in the popularity of four names (both teammates & two additional names) according to the U.S. social security administration  


### Step 1
To view babynames data

```{r}
view(BabyNames)

```
The view() function allows you to see the table including all the variables and cases.
### Step 3
a.) sex and count  is not included in the graph but in the data

b.) count is changed to popularity 

### Step 4
a.) cases have been filtered because there are only 3 cases shown.

b.) there are only male names that appear

c.) popularity is the only new variable, and its relationship is with count in the raw data

### Step 5
step 1: assaign a new variable GlyphReadyForm

step 2: filter the baby names franklin, woodrow, abraham using contain

step 3: select only the variables name, sex, year, and total


### Step 7
```{r}

GlyphReadyForm <-
 BabyNames %>%
   mutate(total= count/500) %>%
  filter(sex =="F")%>%
  filter(name %in% c("Eric", "Mary",  "Emma", "Cora"))%>%
select(name,sex,year,total)
view(GlyphReadyForm)

GlyphReadyForm %>% 
  ggplot(aes(x = year, y = total, group = name)) +
  geom_line( size = 1, alpha = 0.5, aes(color = name)) +
  ylab("Popularity") + xlab("Year")

```





